---
title: "Simple document"
output: html_document
---

I'm an R Markdown document! 

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.

Let's import the FAS__litters.csv

```{r}
library(tidyverse)
```

Let's import the `FAS__litters.csv` csv.

```{r}
litters_df =
  read_csv("data_import_examples/FAS_litters.csv")
litters_df=
  janitor::clean_names(litters_df) #loweruppercase union and clean special characters
```
Import the same dataset using an absolute path. 

```{r}
litters_df_abs=
  read_csv("~/Desktop/data science/data_wrangling_i/data_import_examples/FAS_litters.csv")
names(litters_df_abs)
litters_data=janitor::clean_names(litters_df_abs) #package::function syntax allowes using funciton without loading library
names(litters_data)
```

```{r}
pups_df=
  read_csv("data_import_examples/FAS_pups.csv")

pups_df=
  janitor::clean_names(pups_df)
```

## LOOK AT DATA

```{r}
litters_df
head(litters_df)
tail(litters_df)
```

you can use `view`, don't include in RMD file, run in console only 

```{r, eval=FALSE}
view(litters_df)
```

Look at a data summary
```{r}
str(litters_df)
skimr::skim(litters_data)
litters_df=
  read_csv(
    "data_import_examples/FAS_litters.csv",
    col_types=
      cols(
        Group = col_character(),
    `Litter Number` = col_character(),
    `GD0 weight` = col_double(),
    `GD18 weight` = col_double(),
    `GD of Birth` = col_integer(),
    `Pups born alive` = col_integer(),
    `Pups dead @ birth` = col_integer(),
    `Pups survive` = col_integer()
      )
  )
```
```{r}
library(readxl)
mlb_df =
  read_excel("data_import_examples/mlb11.xlsx")
```

```{r}
pups_base = read.csv("./data_import_examples/FAS_pups.csv")
pups_readr = read_csv("./data_import_examples/FAS_pups.csv")

View(pups_base)
View(pups_readr)

pups_base
pups_readr

pups_base$S
pups_readr$S
```

```{r}
pups_data=read_csv("./data_import_examples/FAS_pups.csv")
pups_df_cleaned=
  janitor::clean_names(pups_data)
write_csv(pups_df_cleaned,"data_import_examples/pups_cleaned.csv")
```

